Refinements for Open Automata

### 2023-06-22 2021-Refinement/paper/refinementarticleV2.tex
intro???

The refinement concept also plays  an important role in software engineering. In addition to helping to cope with the complexity of requirements and design, refinement provides a foundation for ensuring  system (software) correctness. The correctness of a system can
be established by proving, that a system refines its specification.
%Refinement relations verify that an implementation satisfies some properties with respect to a specification. 
Refinement entails that one system  can be considered as a more precise version of another one that is considered to be the specification. The refined model features all the specified behaviours with more concrete details. From a formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.  \RAB{The refinement approach provides mechanism for transforming high-level processes into concrete processes (i.e. implementation), in such a way that some behavioural properties are preserved within the transformation.} \st{semantic treatment  offers specific guarantees on the  behavioural properties of the specification, and it ensures that all behaviours of the specification must belong to the behaviours of the implementation.} Most  refinement work focused on  the study  of  closed
systems \LUDO{\st{which definition?}}, i.e.  systems whose behaviour is fully defined. It is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.

>>>>

The refinement concept also plays  an important role in software engineering. In addition to helping to cope with the complexity of requirements and design, refinement provides a foundation for ensuring  system (software) correctness. The correctness of a system can
be established by proving, that a system refines its specification.
%Refinement relations verify that an implementation satisfies some properties with respect to a specification. 
Refinement entails that one system  can be considered as a more precise version of another one that is considered to be the specification. The refined model features all the specified behaviours with more concrete details. From a formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.  Refinement is an approach that specifies how to transform an abstract or coarse-grain specification of a process into a concrete finer grain view of this process while maintaining some desirable properties.
Most  refinement work focused on  the study  of  closed
systems , i.e.  systems whose behaviour is fully defined. \LUDO{revoir la fin a mon avis: si on veut se distinguer des travaux composants, il faut expliquer} 
However, adopting a refinement approach in an open system that will later interact 
It is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
